NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-05 Manuscript/manuscriptPS.tex

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data was collected using
the Open Collaboration method \cite{botan15}.
The NMRlipids project blog (\url{www.nmrlipids.blogspot.fi}) and
the GitHub repository (\url{www.github.com/NMRLipids/NMRlipidsIVotherHGs})
were used as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS systems without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS systems with various ions concentrations).
Further simulation details are given in the SI.
The simulation data is also indexed in the
searchable database (\url{www.nmrlipids.fi}),
and in the NMRlipids/MATCH GitHub repository (\url{https://github.com/NMRLipids/MATCH}).

The C-H bond order parameters were calculated directly
from the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C-H bond and the membrane normal.
Angular brackets point to the average over all sampled configurations.
The order parameters were first calculated averaging over time separately
for each lipid molecule in the system. The average and
the standard error of the mean were then calculated over different lipids.
The python program ({\it scripts/calcOrderParameters.py}) utilizing
MDAnalysis library \cite{agrawal11,gowers16} is available in Ref. \citenum{MATCHgit}. 
The number density profiles were calculated using {\it gmx density} tool
from Gromacs sofware package \cite{gromacsMANUAL}.

>>>>

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data were collected using
the Open Collaboration method \cite{botan15}, with
the NMR\-lipids Project blog (\url{nmrlipids.blogspot.fi}) and
GitHub repository (\url{github.com/NMRlipids/NMRlipidsIVotherHGs})
as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS bilayers without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS bilayers at various salt concentrations).
Further simulation details are given in the SI.
The simulation data are also indexed in a
searchable database available at \url{www.nmrlipids.fi},
and in the NMRlipids/MATCH repository (\url{github.com/NMRlipids/MATCH}).

The C--H bond order parameters were calculated directly
from the carbon and hydrogen positions using the definition
\begin{equation}
S_{\rm CH}=\frac{1}{2}\langle 3\cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the C--H bond and the membrane normal
(taken to align with $z$, with bilayer periodic in the $xy$-plane).
Angular brackets denote average over all sampled configurations.
The order parameters were first calculated averaging over time separately
for each lipid in the system. The average and
the standard error of the mean were then calculated over different lipids.
Python program ({\tt scripts/calcOrderParameters.py}) that uses the
MDAnalysis library \cite{agrawal11,gowers16} is available in Ref. \citenum{MATCHgit}. 
The number density profiles were calculated using the {\tt gmx density} tool
of the Gromacs sofware package \cite{gromacsMANUAL}.
